ms_0_intro

### 2017-08-25 man/ms_0_intro.Rmd
update intro and references

@@

@@

>>>>

Major drought episodes in the IP were recorded in 1981, 1995, 2000 and 2005 [@VicenteSerrano2014]

@@

frecuencia de las sequías severas (ver Dai 2011)

Algunos eventos extremos han aumentado su frecuencia en los últimos años

@@

Extreme climate events (as droughts, heatwaves) severely affect forests and grasslands throuhg changes in plant physiology, phenology and carbon allocation [@Ummenhofer2017].

Droughts are most likely to have the largest and most long-lasting impacts globally due to large indirect and lagged impacts and long recovery especially for forest ecosystems (ver  18 en @Ummenhofer2017)
